%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Scrum Master (Off-shore team lead)} % Job title
    {Tata Consultancy Services (for American Express)} % Organization
    {Bangalore, India} % Location
    {Mar. 2018 - Mar. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Organized and facilitated scrum ceremonies - daily standups, sprint planning, sprint review, and retrospective to deliver enhancements and new integrations for access management team.}
        \item {Ran a kanban board to handle regular support activities in a first-in-first-out model for high velocity tasks.}
        \item {Managed product backlog and release planning with product owners to ensure monthly and quarterly release cycles.}
        \item {Technically ensure capacity planning for infrastructure by understanding performance of servers in current architecture.}
        \item {Technical reviewer for change management on environments to ensure minimal impact of changes on existing system architecture.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {System Engineer} % Job title
    {Tata Consultancy Services (for American Express)} % Organization
    {Bangalore, India} % Location
    {Mar. 2016 - Mar. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development, maintenance and implementation for CA SiteMinder product suite - Policy Server, Web Agent and CA Federation.}
        \item {Configuration of policy servers for upgrades, certification renewal and rotation.}
        \item {Integrating applications to OAuth2 flow for several environments (development, quality assurance and production).}
        \item {Built proficiency in tools such as Splunk, CA APM, HP sitescope, Oracle Goldengate, Dynatrace to analyse server traffic and incident resolution.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
